Kernel Development Using Rust: A Systematic Literature Review

### 2024-05-24 paper.tex
Update on Overleaf.

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002944.10011122.10002945</concept_id>
<concept_desc>General and reference~Surveys and overviews</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011008.10011024</concept_id>
<concept_desc>Software and its engineering~Language features</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010520.10010521</concept_id>
<concept_desc>Computer systems organization~Architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

Once we had our initial collection of papers from the databases we merged all duplicate papers into one record and then started our first pass which consisted of reading the title and abstract and either marking the paper as \textit{include} or \textit{exclude}. Once  the initial screening was completed we were left with 28 potential papers that we needed an in depth reading.

@@

\begin{table}
    \begin{tabular}{||l|l|l||}
    \hline
    Approach & Papers & Operating System in Rust\\
    \hline\hline
    Monolithic  & \cite{The_kernel_development_community_undated-iw}, \cite{Li2019-ru}, \cite{Miller2021-pg} & \href{https://docs.kernel.org/rust/}{Linux kernel v6.1+}\\
    Micro-kernel & \cite{Chen2023-wb},\cite{Liang2021-bo}, \cite{Liu2024-xe} \cite{} & Atmosphere, Redox, Redleaf\\
    Embedded & \cite{Culic2022-bk} & \href{https://github.com/tock/tock}{Tock}, \href{https://hubris.oxide.computer/}{Hubris}, \href{https://www.drone-os.com/}{Drone}, \href{https://bern-rtos.org/}{Bern} \\
    Unikernel & \cite{Lankes2019-cm},  \cite{Boos2020-zh}, \cite{Ijaz2023-da}  & RustyHermit, Theseus \\
    Exokernel & \cite{Li2024-yb} & W-Kernel \\
    \hline
  \end{tabular}
  \caption{Approaches and Methodologies for Rust in the Kernel}
    \label{tab:RQ1}
\end{table}

>>>>

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002944.10011122.10002945</concept_id>
<concept_desc>General and reference~Surveys and overviews</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011008.10011024</concept_id>
<concept_desc>Software and its engineering~Language features</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010520.10010521</concept_id>
<concept_desc>Computer systems organization~Architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

Once we had our initial collection of papers from the databases we merged all duplicate papers into one record and then started our first pass which consisted of reading the title and abstract and either marking the paper as \textit{include} or \textit{exclude}. Once  the initial screening was completed we were left with 26 potential papers that we needed an in depth reading.

@@

\begin{table}
    \begin{tabular}{||l|l|l||}
    \hline
    Approach & Papers & Operating System in Rust\\
    \hline\hline
    Monolithic  & \cite{The_kernel_development_community_undated-iw}, \cite{Li2019-ru}, \cite{Miller2021-pg}, \cite{Oikawa2023-ms} & \href{https://docs.kernel.org/rust/}{Linux kernel v6.1+}\\
    Micro-kernel & \cite{Chen2023-wb},\cite{Liang2021-bo}, \cite{Liu2024-xe}, \cite{Narayanan2020-gs}, \cite{Narayanan2019-fd} & Atmosphere, Redox, Redleaf\\
    Embedded & \cite{Culic2022-bk}, \cite{Vishnunaryan2022-yd} & \href{https://github.com/tock/tock}{Tock}, \href{https://hubris.oxide.computer/}{Hubris}, \href{https://www.drone-os.com/}{Drone}, \href{https://bern-rtos.org/}{Bern}, HarSaRK \\
    Unikernel & \cite{Lankes2019-cm},  \cite{Boos2020-zh}, \cite{Ijaz2023-da}, \cite{Sung2020-bb}  & RustyHermit, Theseus \\
    Exokernel & \cite{Li2024-yb} & W-Kernel \\
    \hline
  \end{tabular}
  \caption{Approaches and Methodologies for Rust in the Kernel}
    \label{tab:RQ1}
\end{table}
